opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-28 chapters/01_introduction.tex
Added definition of transfer learning/style transfer

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality. In this way, one can bring the simulated patterns closer to those observed in experiments by more accurately modeling the scattering process. Improving the simulation of data involves accounting for more of the physical effects that influence the scattering process such as preferred grain orientation, variations in grain size, crystal defects, the impact of temperature on the scattering process, internal stress, and X-ray-induced fluorescence. \cite{cao2024simxrd} Additionally, it should be considered that varying experimental setups can produce distinct powder diffraction patterns on the same sample. Features that may vary between experimental setups and influence the recorded pattern include the shape of diffraction peaks, the wavelength and polarization of the employed X-ray source, and the detector geometry. Some experimental setups may also exhibit imperfections such as displacement of the sample from its intended position leading to the recorded scattering angles being slightly erroneous or background events originating from instrument noise or  X-rays scattering off equipment onto the screen.\\

Additionally, some of the observed imperfections, such as background and noise, can be modeled using machine-learning approaches. This is similar to the concept of style transfer\cite{Gatys2016, Ganin2015} found in the domain of machine learning applied to images. Here, the objective is to obtain a classification or regression model when only labeled images of one style (simulated data) and unlabeled or partially labeled images of another style (experimental data) are available. \\

@@

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis.
We hope that this will yield more advanced automated ML approaches in the future, which can readily be applied in high-throughput experimentation pipelines.

>>>>

Furthermore, even completely unlabeled data can enable machine learning researchers to evaluate how closely their simulations represent experimental data, identify what features are missing, and modify their simulation algorithms accordingly to arrive at a simulation that mirrors how data appears in reality. In this way, one can bring the simulated patterns closer to those observed in experiments by more accurately modeling the scattering process.
Improving the simulation of data involves accounting for more of the physical effects that influence the scattering process such as preferred grain orientation, variations in grain size, crystal defects, the impact of temperature on the scattering process, internal stress, and X-ray-induced fluorescence\cite{cao2024simxrd, Waseda2011, Pecharsky2023}.  Additionally, it should be considered that varying experimental setups can produce distinct powder diffraction patterns on the same sample. Features that may vary between experimental setups and influence the recorded pattern include the shape of diffraction peaks, the wavelength and polarization of the employed X-ray source, and the detector geometry
\cite{Waseda2011, Pecharsky2023}. Some experimental setups may also exhibit imperfections such as displacement of the sample from its intended position leading to the recorded scattering angles being slightly erroneous \cite{hulbert2023} or background events originating from instrument noise or X-rays scattering off equipment onto the screen.\\

Additionally, some of the observed imperfections, such as background and noise, can be accounted for using transfer learning approaches. In transfer learning the objective is to transfer the capabilities of a model learned on a source domain in which labeled data is abundant to a target domain in which labeled data is sparse\cite{Zhuang2021}. In this context, the source domain is simulated powder diffraction patterns and the target domain is experimental powder diffraction patterns. Many approaches to transfer learning have been proposed, particularly in the domain of image classification \cite{Gatys2016, Ganin2015}. These existing techniques could potentially be adapted to facilitate transfer learning in the context of pXRD patterns.

@@

The broad range of available experimental samples contained in the opXRD v1.0 database makes it possible to apply state-of-the-art ML approaches to the domain of powder XRD analysis. Sharing raw powder diffraction data is in the interest of 
We hope that this will yield more advanced automated ML approaches in the future, which can readily be applied in high-throughput experimentation pipelines.

### 2024-11-28 chapters/04_our_dataset.tex
Added definition of transfer learning/style transfer

We will continue growing the opXRD dataset, thus additional contributors are very welcome to contact us and submit data through the website. To find out more about how to contribute to this dataset, visit our website \footnote{Datasets can be contributed to opXRD under \url{https://xrd.aimat.science}.} specially designed to collect this dataset.

>>>>

We will continue growing the opXRD dataset, thus additional contributors are very welcome to contact us and submit data through the website. To find out more about how to contribute to this dataset, visit our website\footnote{Datasets can be contributed to opXRD under \url{https://xrd.aimat.science}.} specially designed to collect this dataset.
